### 2020-08-17 design.tex
new version

\subsection{Design Principle}
To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
%\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}

\begin{itemize}
    \item \textbf{Layered architecture and frequent introduction of input.} In our architecture all input images are processed simultaneously and separately, with the information from other images for reference, throughout the network. The initial input images are introduced into the dataflow at each layer, from beginning to end, forming a model with uneven depth, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
    \item \textbf{Merging layers to adapt multiple frames.} A merging process inside each layer functions as the revenue of communication across images integrates information from all the images into one, the result of which is then stacked with each image for the next convolution. At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
    \item \textbf{Inconsistency problem, model Complexity and adaption for variable input.} To counter the lack of consistency between frames, all the convolutional layers throughout the network are performed individually for each image with the same set of parameters. This not only reduces parameter count and calculation power, but also avoids reliance on consistency between neighboring frames. Furthermore, this allows variations in the number of input images.
    \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of deviation and producing 'fake' results. The frequent introduction of input images is designed to mitigate this challenge. Also, instead of using Mean Square Error(MSE) as the loss function, we put a weight on each pixel before applying weighted MSE. Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighboring dark pixels so that long strokes and intersections of strokes are given higher weights. This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests. 
  \end{itemize}

@@

%\cl{$H(\cdot)$ or $H(\cdot,\cdot)$?}
\begin{figure}
    \centering
       \includegraphics[width=0.5\textwidth]{./pic/network.pdf}
       \caption{Core network architecture of SRPeek.}
       \label{fig-system}
   \end{figure}

>>>>

\subsection{Design Principle}
To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-system}.
%\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Layered architecture and frequent introduction of input.} In our architecture all input images are processed simultaneously and separately, with the information from other images for reference, throughout the network. The initial input images are introduced into the dataflow at each layer, from beginning to end, forming a model with uneven depth, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
    \item \textbf{Merging layers to adapt multiple frames.} A merging process inside each layer functions as the revenue of communication across images integrates information from all the images into one, the result of which is then stacked with each image for the next convolution. At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
    \item \textbf{Inconsistency problem, model Complexity and adaption for variable input.} To counter the lack of consistency between frames, all the convolutional layers throughout the network are performed individually for each image with the same set of parameters. This not only reduces parameter count and calculation power, but also avoids reliance on consistency between neighboring frames. Furthermore, this allows variations in the number of input images.
    \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of deviation and producing 'fake' results. The frequent introduction of input images is designed to mitigate this challenge. Also, instead of using Mean Square Error(MSE) as the loss function, we put a weight on each pixel before applying weighted MSE. Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighboring dark pixels so that long strokes and intersections of strokes are given higher weights. This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests. 
  \end{itemize}

@@

%\cl{$H(\cdot)$ or $H(\cdot,\cdot)$?}
\begin{figure}
    \centering
       \includegraphics[width=0.90\linewidth]{./pic/network.pdf}
       \caption{Core network architecture of SRPeek.}
       \label{fig-system}
   \end{figure}

### 2020-08-17 evaluation.tex
new version

\section{Model Evaluation}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We evaluate the performance of the network model in different training and testing conditions. We perform the following experiments with two Custom Off-The-Shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possess up to 5x optical zooming ability which we will utilize fully in our experiments.

@@

\begin{table}[!t]
    \centering
    \caption{Recognition accuracy in various scenarios.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    Scenarios & Home & Transport & Theater \\ \midrule
    Baseline & 5\% & 0 & 0\\ 
    \midrule
    OCR & 100\% & 10\% & 23\%\\ 
    Human & 95\% & 85\% & 70\%\\ \bottomrule
    \end{tabular}
    \label{table-scenarios}
\end{table}

@@

\begin{table}[!t] 
    \centering
    \caption{Impact of hand tremors when the camera (attacker phone) and/or target (victim phone) is handheld.}
    \begin{tabular}{ccccc}
        \toprule
    Accuracy & None & Camera & Target & Both  \\
    \midrule
    Baseline & 5\% & 0 & 5\% & 5\%\\ 
    \midrule
    OCR & 95\% & 85\% & 80\% & 80\%\\ 
    Human & 95\% & 85\% & 80\% & 85\%\\ \bottomrule
    \end{tabular}
    \label{table-tremor}
\end{table}

>>>>

\section{Model Evaluation}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We evaluate the performance of the network model in different training and testing conditions. We perform the following experiments with two commercial off-the-shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possess up to 5x optical zooming ability which we will utilize fully in our experiments.

@@

\begin{table}[!t]
    \centering
    \caption{Recognition accuracy in various scenarios.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    Scenarios & Home & Transport & Theater \\ \midrule
    Naked Eye & 5\% & 0 & 0\\ 
    \midrule
    OCR & 100\% & 10\% & 23\%\\ 
    Human & 95\% & 85\% & 70\%\\ \bottomrule
    \end{tabular}
    \label{table-scenarios}
\end{table}

@@

\begin{table}[!t] 
    \centering
    \caption{Impact of hand tremors when the camera (attacker phone) and/or target (victim phone) is handheld.}
    \begin{tabular}{ccccc}
        \toprule
    Accuracy & None & Camera & Target & Both  \\
    \midrule
    Naked Eye & 5\% & 0 & 5\% & 5\%\\ 
    \midrule
    OCR & 95\% & 85\% & 80\% & 80\%\\ 
    Human & 95\% & 85\% & 80\% & 85\%\\ \bottomrule
    \end{tabular}
    \label{table-tremor}
\end{table}

### 2020-08-17 implementation.tex
9 pages
new version

\subsection{Experiment Setting}
\label{sec-experiment-setting}
Our experiment consists of 2 smartphones, one for the attacker and one the victim. Their distance is between 1 and 2 meters for traditional lenses (for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming. Both phones are fixed to stands to keep them completely still, but the lenses with optical zoom will shift slightly time to time, which can simulate a handheld situation. An app runs inside the attacker's phone, taking photos in burst mode repeatedly (20 photos per burst), and another app runs inside the victim's phone, displaying random characters with random fonts and colors. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this character assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters. Screenshots were taken in the victim's phone as ground truth for training and evaluation. An illustration of our experimental setting is displayed in Fig.~\ref{illustration_of_system}.
\begin{figure}
	\centering
	\includegraphics[width=0.46\textwidth]{pic/setup.pdf}
    \caption{Illustration of our experimental setting (distance between phones is shortened for demonstration).}
	\label{illustration_of_system}
\end{figure}
% \begin{figure}
%   \centering
%      \centering
%      \subfigure[Experiment setting. Distance between phones are shortened for demonstration.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp1.jpg}
%          \label{fig-exp1}
%          }
%    \subfigure[screenshot from attacker's phone(SRPeek system).]{
%          \includegraphics[width=0.5\textwidth]{pic/exp2.jpg}
%          \label{fig-exp2}
%          }
%    \subfigure[screenshot from victim's phone.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp3.jpg}
%          \label{fig-exp3}
%          }
%      \caption{Illustration of our experimental setting.}
%      \label{fig-experiment}
% \end{figure}

@@

Our model accepts 20 images at a time, with a size of 9x9 pixels. The model consists of 5 blocks described in the previous section. In each block, feature maps from the previous layer are passed through a single convolutional layer with 32 channels of feature maps as output. the 20x32 feature maps are then merged horizontally with the max-min-average process, and the output is 5x32 channels. Simultaneously, the original input images are processed again with a single convolutional layer with 32 channels output, and stacked with the former 5x32 channels to form a dataflow of 6x32 channels for each one of the 20 images. These channels are finally passed through a single convolutional layer, outputting 32 channels per image for the next block. The kernels in each convolutional layer is 3x3. We also insert LeakyReLU and Batch Normalization processes after each convolutional layer, and 2 upsampling layers between the 5 blocks. A single 1x1 convolutional layer is placed after the 5 blocks with a single channel as output to form the final output layer. This model consists of approximately 200,000 parameters and a complexity of about 400,000 FLOPs. As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9x9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.

>>>>

\subsection{Experiment Setting}
\label{sec-experiment-setting}
Our experiment consists of 2 smartphones, one for the attacker and one the victim. Their distance is between 1 and 2 meters for traditional lens and 5 to 7.5 meters for optical lens. Both phones are fixed to stands to keep them completely still, but the lenses with optical zoom will shift slightly time to time, which can simulate a handheld situation. An app runs inside the attacker's phone, taking photos in burst mode repeatedly (no more than 20 photos per burst), and another app runs inside the victim's phone, displaying random characters with random fonts and colors. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this character assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters. Screenshots were taken in the victim's phone as ground truth for training and evaluation. An illustration of our experimental setting is displayed in Fig.~\ref{illustration_of_system}.
\begin{figure}
	\centering
	\includegraphics[width=0.80\linewidth]{pic/setup.pdf}
    \caption{Illustration of our experimental setting (distance between phones is shortened for demonstration).}
	\label{illustration_of_system}
\end{figure}
% \begin{figure}
%   \centering
%      \centering
%      \subfigure[Experiment setting. Distance between phones are shortened for demonstration.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp1.jpg}
%          \label{fig-exp1}
%          }
%    \subfigure[screenshot from attacker's phone(SRPeek system).]{
%          \includegraphics[width=0.5\textwidth]{pic/exp2.jpg}
%          \label{fig-exp2}
%          }
%    \subfigure[screenshot from victim's phone.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp3.jpg}
%          \label{fig-exp3}
%          }
%      \caption{Illustration of our experimental setting.}
%      \label{fig-experiment}
% \end{figure}

@@

Our model accepts any number of images per burst, but it can only process a patch of 9$\times$9 pixels(not necessarily containing whole characters, as it functions at the strokes level) at a time. We expect that characters should be upright(the attacker can simply spin his phone). The model consists of 5 blocks described in the previous section. In each block, feature maps from the previous layer are passed through a single convolutional layer with 32 channels of feature maps as output. the 20$\times$32 feature maps are then merged horizontally with the max-min-average process, and the output is 5$\times$32 channels. Simultaneously, the original input images are processed again with a single convolutional layer with 32 channels output, and stacked with the former 5$\times$32 channels to form a dataflow of 6$\times$32 channels for each one of the images. These channels are finally passed through a single convolutional layer, outputting 32 channels per image for the next block. The kernels in each convolutional layer is 3$\times$3. We also insert LeakyReLU and Batch Normalization processes after each convolutional layer, and 2 upsampling layers between the 5 blocks. A single 1$\times$1 convolutional layer is placed after the 5 blocks with a single channel as output to form the final output layer. This model consists of approximately 200,000 parameters and a complexity of about 400,000 FLOPs. As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9$\times$9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.

### 2020-08-17 introduction.tex
new version

\vspace{1mm}
\noindent
\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{overview}. 
While the victim's reading private information in public, the attacker uses his commercial smartphone to take 10 to 20 snapshots rapidly of his screen in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result. The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously, not missing any detail. Meanwhile, few people would suspect a stranger holding his smartphone at 1.8 meters behind them. Given the newest generation of smartphones equipped with telephoto lenses and capable of optical zooming, this distance can reach a staggering 6 meters, posing a silent but deadly threat to screen privacy.

>>>>

\vspace{1mm}
\noindent
\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{overview}. 
While the victim's reading private information in public, the attacker, given that he/she has line of sight of the screen, uses his commercial smartphone to take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result. The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously. Meanwhile, few people would suspect a stranger holding his smartphone at 1.8 meters behind them. Given the newest generation of smartphones equipped with telephoto lenses and capable of optical zooming, this distance can reach a staggering 6 meters, posing a silent but deadly threat to screen privacy.

### 2020-08-17 system_overview.tex
new version

\vspace{1mm}
\noindent
\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing to reduce the workload of the network. The characters are normally around 10x10 pixels, while variations in size aren't influential as they're covered in the training data, so zooming isn't necessary.

\vspace{1mm}
\noindent
\textbf{Processing:} As our SR network accepts only 9x9 patches, we will process all the 9x9 patches (with overlapping) among the input photo to generate 36x36 images (4x upscaling). The input is RGB colored, while the output, as we are not interested in color, is black and white. The three calculation processes (Alignment, Adjustment, Processing) run parallel to the input process, so that the attacker can process a batch of images while the next batch is being collected simultaneously.

\vspace{1mm}
\noindent
\textbf{Output:} The outputs of our SR network, the 36x36 overlapping patches, are then rearranged to their original locations and merged (using average values) into a single image. As we only carve out the texts for processing, we will then insert these high-res texts back to their original locations on one of the input images, and display the patched image to the attacker (An illustration of the patched image can be found in Fig.~\ref{illustration_of_system}).

>>>>

\vspace{1mm}
\noindent
\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing to reduce the workload of the network. The character size is normally 10 to 20 pixels, while variations in size aren't influential as they're covered in the training data, so zooming isn't necessary.

\vspace{1mm}
\noindent
\textbf{Processing:} As our SR network accepts only 9$\times$9 patches, we will process all the 9$\times$9 patches (with overlapping) among the input photo to generate 36$\times$36 images (4$\times$ upscaling). The input is RGB colored, while the output, as we are not interested in color, is black and white. The three calculation processes (Alignment, Adjustment, Processing) run parallel to the input process, so that the attacker can process a batch of images while the next batch is being collected simultaneously.

\vspace{1mm}
\noindent
\textbf{Output:} The outputs of our SR network, the 36$\times$36 overlapping patches, are then rearranged to their original locations and merged (using average values) into a single image. As we only carve out the texts for processing, we will then insert these high-res texts back to their original locations on one of the input images, and display the patched image to the attacker (An illustration of the patched image can be found in Fig.~\ref{illustration_of_system}).
